Coherent optical creation of a single molecule

### 2020-12-08 paper.tex
Define omega_R

\begin{figure}
  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
  \caption{
    Beampath for generating two frequencies in the tweezer for the Raman transition
    (Some mirrors and other optics used for alignment are not included.)
    Two ASE filters, one directly after the laser source and one after both optical fibers, are used. The laser source is a fiber amplifier seeded by a external cavity diode laser.
    The red beam path is the $0$-th order of the double pass~(DP) AOM which is used at all times. 
    The blue beam path is the $1$-st order of the DP AOM, and generates the second frequency required to drive the Raman transition.
    %When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
    %(blue beam path) which generates the required frequency different to drive
    %the Raman transition. 
    %The two frequencies are recombined on the DP AOM.
    The $0$-th order light is shifted by another single pass~(SP) AOM before recombining, which ensures that it will not interfere with the leak light from the DP AOM, resulting in power fluctuations. 
    %be at the same frequency
    %as the $0$-th order light which can cause a significant power fluctuation
    %due to interference.
    The experiment typically starts with the SP AOM on and the DP AOM off.
    When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
    to achieve the desired power at both frequencies, while keeping the total power fixed. 
    \label{f-beampath}
  }
\end{figure}

@@

\begin{figure*}[t!]
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer power and detuning.
    (a) The Raman resonance fitted by $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are the power ($P$) dependent background and $v'=0$ contributions
    to the light shift and
    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
    the $v'=0$ resonance frequency $f_0$.
    $a_P$ is fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
    $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}

>>>>

\begin{figure}
  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
  \caption{
    Beampath for generating two frequencies in the tweezer for the Raman transition
    (Some mirrors and other optics used for alignment are not included.)
    Two ASE filters, one directly after the laser source and one after both optical fibers, are used. The laser source is a fiber amplifier seeded by a external cavity diode laser.
    The red beam path is the $0$-th order of the double pass~(DP) AOM which is used at all times.
    The blue beam path is the $1$-st order of the DP AOM, and generates the second frequency required to drive the Raman transition.
    % When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
    % (blue beam path) which generates the required frequency different to drive
    % the Raman transition.
    % The two frequencies are recombined on the DP AOM.
    The $0$-th order light is shifted by another single pass~(SP) AOM before recombining, which ensures that it will not interfere with the leak light from the DP AOM, resulting in power fluctuations.
    % be at the same frequency
    % as the $0$-th order light which can cause a significant power fluctuation
    % due to interference.
    The experiment typically starts with the SP AOM on and the DP AOM off.
    When driving the Raman transition, the RF powers for both AOMs are ramped simultaneously
    to achieve the desired power at both frequencies, while keeping the total power fixed.
    \label{f-beampath}
  }
\end{figure}

@@

\begin{figure*}[t!]
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer power and detuning.
    (a) The Raman resonance~($\omega_R$) fitted by $a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are the power ($P$) dependent background and $v'=0$ contributions
    to the light shift and
    $\Delta\equiv2\pi\times\paren{f_0 - f_{\mathrm{tweezer}}}$ is the detuning from
    the $v'=0$ resonance frequency $f_0$.
    $a_P$ is fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power $\omega_{R0}=2\pi\times770.1969(2)~\mathrm{MHz}$ where the statistical uncertainty is shown.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are the background and $v'=0$ contributions that scale as $P^{1.29}$ with optical power.
    The detuning is calculated from the PA frequency fitted in (a). Fit parameters are listed in Table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing approximate $P^{0.5}$ scaling of $\Omega_m$ and
    $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
